### 2021-04-07 Main_Figures/Global_trait_spectrum.Rmd
Fig 1, 2 and 3 ready. 1 still needs edits on the images... Waiting for the pictures to be made.
Last edits

library(magick)
tree <- image_read("Images/PPCA_Plot/Tree.png")
tree_1 <- as.raster(tree)

@@

selfing_h <- image_read("Images/PPCA_Plot/Selfing_High.png")
selfing_h_1 <- as.raster(selfing_h)

@@

many_flowers <- image_read("Images/PPCA_Plot/Many_Flowers.png")
many_flowers_1 <- as.raster(many_flowers)
#many_flowers_1 <- image_rotate(many_flowers, 45)

large_flower <- image_read("Images/PPCA_Plot/Large_Flower.png")
large_flower_1 <- as.raster(large_flower)

flower_small <- image_read("Images/PPCA_Plot/Flower_Small.png")
flower_small_1 <- as.raster(flower_small)
#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.85,ymin = 2.05, ymax = 3.95)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.7, xmax = -2,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 0.9, ymax = 2.05) +
    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -2.8, ymax = -2.2)

>>>>

library(magick)

#Images were made by Paula Martin
#Check her work on https://paulamartinart.com/

tree <- image_read("Images/PPCA_Plot/Tree.png")
tree_1 <- as.raster(tree)

@@

selfing_h <- image_read("Images/PPCA_Plot/selfing.png")
selfing_h_1 <- as.raster(selfing_h)

@@

many_flowers <- image_read("Images/PPCA_Plot/Inflorescencia.png")
many_flowers_1 <- as.raster(many_flowers)
#many_flowers_1 <- image_rotate(many_flowers, 45)

large_flower <- image_read("Images/PPCA_Plot/flower_big.png")
large_flower_1 <- as.raster(large_flower)

flower_small <- image_read("Images/PPCA_Plot/flower_short.png")
flower_small_1 <- as.raster(flower_small)

herb <- image_read("Images/PPCA_Plot/herb.png")
herb_1 <- as.raster(herb)

#############################################################################################################################################################
#COMPATIBILITY
#############################################################################################################################################################
#Load plots

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.85,ymin = 2.05, ymax = 3.95)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.35,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.25, xmax = 4.25,ymin = 1.2, ymax = 2.45) +
    annotation_raster(flower_small_1, xmin = -3.60, xmax = -2.55,ymin = -2.2, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3.1,ymin = -2.8, ymax = -2)
